---
title: "Global Plastic Treaty Model 01_A1_14"
author: "Nivedita Biyani"
date: "2023-07-17"
output: html_document

Final with textiles 
---

# DESCRIPTION
This code chunk is made using the excel sheet that Dr. Roland Geyer on June 20th 2023 titled 2023227 Global Treatment v12 Plus Additives & Textiles. 

## 1. GOAL
We want to get the following: 
1. Production by region year for fiber 
2. Production by region and by year for resin 
3. Production by region and year for additives (B26) 

### PROCESS FLOW 
 1. **Set Up**
 2. Import
 3. Tidy
 4. Transform 
 5. Visualize 
 6. Model 
 7. Communicate 

```{r, R SET UP}

knitr::opts_chunk$set(echo = TRUE, warning=FALSE) 
library(RcppRoll)
library(corrplot)
library(psych)
library(reshape)
library(dplyr)
library(forcats)
library(ggplot2)
library(tidyverse)
library(viridis)
library(scales) # to access break formatting functions
library(ggalt)
library(plotly)
library(tibble)
library(psych)
library(gdata)
library(data.table)
library(heplots)
library(candisc)
library(car)
library("alluvial")
library("ggalluvial")
library("zoo")
library("magrittr")
library("forecast")
library("imputeTS")
library("zoo")
library("fpp2")
library("fpp")
library("readxl")
library(reprex)
library(purrr)
library(glue)

libs <- c('dplyr', 'stringr', 'forcats',     # wrangling
          'knitr',               # table styling
          'ggplot2','alluvial','ggalluvial')                     # data
invisible(lapply(libs, library, character.only = TRUE))

```

## 2. GOAL
In this section we are importing all the data sets used in the modeling exercise. All data feeds are in one place in the model. 

### PROCESS FLOW 
 1. Set Up
 2. **Import**
 3. Tidy
 4. Transform 
 5. Visualize 
 6. Model 
 7. Communicate 
 
```{r, Reading Data}
one_drive_path <- "/Users/dr.nivedita/Library/CloudStorage/OneDrive-Personal/04_Post-Doc/01.R_Code"

# Base Inputs of Production
options(digits = 8)
A_01_Resin<-read.csv(glue("{one_drive_path}/02_Data_Raw/01_Production_of_Resin_(no_fiber).csv"))
A_02_Fiber<-read.csv(glue("{one_drive_path}/02_Data_Raw/02_Production_Fiber.csv"))
A_03_Add<-read.csv(glue("{one_drive_path}/02_Data_Raw/03_Production_Additives.csv"))

# Base Inputs of Imports 
A_04_Net_Import_Resin<-read.csv(glue("{one_drive_path}/02_Data_Raw/04_Net_Import_Resin_no_fiber_copy.csv"))
A_05_Net_Import_Fiber<-read.csv(glue("{one_drive_path}/02_Data_Raw/05_Net_Import_Fiber_copy.csv"))
A_06_Net_Import_Plastic_Articles<-read.csv(glue("{one_drive_path}/02_Data_Raw/06_Net_import_plastic_articles copy.csv"))
A_07_Net_Import_Finished_Goods<-read.csv(glue("{one_drive_path}/02_Data_Raw/07_Net_Import_plastic_in_finished_goods_no_fiber copy.csv"))

# Trade New versions 12 
AB_01_Trade_China<-read.csv(glue("{one_drive_path}/02_Data_Raw/18_Net_Trade_China.csv"))
AB_02_Trade_NAFTA<-read.csv(glue("{one_drive_path}/02_Data_Raw/19_Net_Trade_NAFTA.csv"))
AB_03_Trade_EU<-read.csv(glue("{one_drive_path}/02_Data_Raw/20_Net_Trade_EU.csv"))
AB_04_Trade_Row<-read.csv(glue("{one_drive_path}/02_Data_Raw/21_Net_Trade_Row.csv"))

# Polymer breakdown by Sector and Region (Sector Polymer Matrices)
# These ones need to be fed in with 5 decimal places to get same values as excel sheet 
AC_01_China<-read.csv(glue("{one_drive_path}/02_Data_Raw/08_China_End_Use_and_Type.csv"))
AC_02_NAFTA<-read.csv(glue("{one_drive_path}/02_Data_Raw/09_NAFTA_End_Use_and_Type.csv"))
AC_03_Europe<-read.csv(glue("{one_drive_path}/02_Data_Raw/10_Europe_End_Use_and_Type.csv"))
AC_04_Row<-read.csv(glue("{one_drive_path}/02_Data_Raw/11_RoW_End_Use_and_Type.csv"))

# Polymer breakdown by Sector and Region Part #2 (Sector Polymer Matrices)
# These ones need to be fed in with 5 decimal places to get same values as excel sheet 
AC_01_China2<-read.csv(glue("{one_drive_path}/02_Data_Raw/08.1_China_End_Use_and_Type.csv"))
AC_02_NAFTA2<-read.csv(glue("{one_drive_path}/02_Data_Raw/09.1_NAFTA_End_Use_and_Type.csv"))
AC_03_Europe2<-read.csv(glue("{one_drive_path}/02_Data_Raw/10.1_Europe_End_Use_and_Type.csv"))
AC_04_Row2<-read.csv(glue("{one_drive_path}/02_Data_Raw/11.1_RoW_End_Use_and_Type.csv"))

# Textiles as it is its own thing 1950-2003
AD<-read.csv(glue("{one_drive_path}/06_Output/06_Output\\KA5.csv"))

# Lifetime distributions 
AI_02<-read.csv(glue("{one_drive_path}/02_Data_Raw/12_Lifetime copy.csv"))

# 1950 ~ 2004 History Curve Fitting
AHH1<-read.csv(glue("{one_drive_path}/02_Data_Raw/13_1950-2004 copy.csv"))

# End of Life Breakdowns 
AKE_Eol_China<-read.csv(glue("{one_drive_path}/02_Data_Raw/14_Eol_China copy.csv"))
AKE_Eol_EU<-read.csv(glue("{one_drive_path}/02_Data_Raw/15_Eol_EU copy.csv"))
AKE_Eol_NAFTA<-read.csv(glue("{one_drive_path}/02_Data_Raw/16_Eol_NAFTA copy.csv"))
AKE_Eol_Row<-read.csv(glue("{one_drive_path}/02_Data_Raw/17_Eol_RoW copy.csv"))

```

## 3. GOAL 
In this section we are making all the data long form, even data that we use later in the model. 

### PROCESS FLOW 
 1. Import
 2. **Tidy**
 3. Transform 
 4. Visualize 
 5. Model 
 6. Communicate 
 
## EXTRAS: 
 - I tried using lapply to repeat the same function over multiple data frames, but it did not work. Would be good to make this code shorter.

```{r, Making it Long Form }

B_01_Resin<-A_01_Resin %>% pivot_longer(cols=c('China',"NAFTA","EU30","RoW"),
                                          names_to='Region',
                                          values_to='MT_Plastic_Prod_Resin')

B_02_Fiber<-A_02_Fiber %>% pivot_longer(cols=c('China',"NAFTA","EU30","RoW"),
                    names_to='Region',
                    values_to='MT_Plastic_Prod_Fiber')

B_03_Additives<-A_03_Add %>% pivot_longer(cols=c('China',"NAFTA","EU30","RoW"),
                                              names_to='Region',
                                              values_to='MT_Add')

B_04_Net_Import_Resin<-A_04_Net_Import_Resin %>% pivot_longer(cols=c('China',"NAFTA","EU30","RoW"),
                                                  names_to='Region',
                                                  values_to='MT_Plastic_Import_Resin_no_Fiber')

B_05_Net_Import_Fiber<-A_05_Net_Import_Fiber %>% pivot_longer(cols= c('China',"NAFTA","EU30", "RoW"),
                                                              names_to="Region",
                                                              values_to="MT_Import_Fiber")

B_06_Net_Import_Plastic_Article<-A_06_Net_Import_Plastic_Articles %>%pivot_longer(cols=c('China',"NAFTA","EU30","RoW"),
                                                          names_to='Region',
                                                          values_to='MT_Plastic_Import_Plast_Artic')

  
B_07_Net_Import_Finished_Goods<-A_07_Net_Import_Finished_Goods %>% pivot_longer(cols=c('China',"NAFTA","EU30","RoW"),
                                                         names_to='Region',
                                                         values_to='MT_Plastic_Import_Plast_Finished_Goods')

#############################################################
#############################################################
#  Making All Long form Data into 1 Mother Data Set        ##
#############################################################
#############################################################

# Use Merge When Column are the Same 

B1<-B_02_Fiber %>% inner_join(B_01_Resin, 
                                       by=c('Year'="Year","Region"="Region"))

B2<-B1 %>% inner_join(B_04_Net_Import_Resin,
                      by=c("Year"="Year",'Region'="Region"))

B3<-B2 %>% inner_join(B_06_Net_Import_Plastic_Article,
                       by=c("Year"="Year", "Region"="Region"))
  
B4<-B3 %>% inner_join(B_07_Net_Import_Finished_Goods,
                      by=c("Year"="Year","Region"="Region"))

B5<-B4 %>% inner_join(B_03_Additives,
                      by=c("Year"="Year", "Region"="Region"))

B5<-B5 %>% inner_join(B_05_Net_Import_Fiber,
                      by=c("Year"="Year", "Region"="Region"))


#############################################################
#############################################################
#                         Mother Data Set                  ##
#############################################################
#############################################################

# B5 Is Mother Data set for Production of Plastic

#############################################################
#############################################################
#               Making it long form                        ##
# i = Time (16) = Years 
# j = Country (4) = China, NAFTA, EU30, or RoW
# k = Sector (7) = Transportation or Packaging or Building and Construction and Electrical and Electronic or Household_Leisure_Sports 
# or Agriculture or Other 
# l = Type (9)= LLDPE_LDPE or HDPE or PP or PS or PVC or PET or PUR or "Other Thermoplastics" or "Other Thermosets"
#                                                          ##
#############################################################
#############################################################

##### CHINA #####

C_01_China_Long<-AC_01_China %>% pivot_longer(cols=c('LLDPE_LDPE',"HDPE","PP","PS","PVC","PET","PUR","Other.Thermoplastics","Other.Thermosets","Sum"),
                                             names_to='Type',
                                             values_to='Percentage')
C_01_China_Long<-C_01_China_Long %>% 
  add_column(Region = "China")

C_01_China_Long<-C_01_China_Long[c("Region","Major_Market_Sector","Type","Percentage")]


##### NAFTA #####
C_02_NAFTA_Long<-AC_02_NAFTA %>% pivot_longer(cols=c('LLDPE_LDPE',"HDPE","PP","PS","PVC","PET","PUR","Other.Thermoplastics","Other.Thermosets","Sum"),
                                             names_to='Type',
                                             values_to='Percentage')
C_02_NAFTA_Long<-C_02_NAFTA_Long %>% 
  add_column(Region = "NAFTA")

C_02_NAFTA_Long<-C_02_NAFTA_Long[c("Region","Major_Market_Sector","Type","Percentage")]


##### EU30 #####

C_03_EU30_Long<-AC_03_Europe %>% pivot_longer(cols=c('LLDPE_LDPE',"HDPE","PP","PS","PVC","PET","PUR","Other.Thermoplastics","Other.Thermosets","Sum"),
                                             names_to='Type',
                                             values_to='Percentage')
C_03_EU30_Long<-C_03_EU30_Long %>% 
  add_column(Region = "EU30")

C_03_EU30_Long<-C_03_EU30_Long[c("Region","Major_Market_Sector","Type","Percentage")]

##### RoW #####

C_04_RoW_Long<-AC_04_Row %>% pivot_longer(cols=c('LLDPE_LDPE',"HDPE","PP","PS","PVC","PET","PUR","Other.Thermoplastics","Other.Thermosets","Sum"),
                                         names_to='Type',
                                         values_to='Percentage')
C_04_RoW_Long<-C_04_RoW_Long %>% 
  add_column(Region = "RoW")

C_04_RoW_Long<-C_04_RoW_Long[c("Region","Major_Market_Sector","Type","Percentage")]

```

## 4. GOAL 
Combining columns for percentage of each type of plastic. This data frame is actually not used for a while. 

### PROCESS FLOW 
 1. Import
 2. **Tidy**
 3. Transform 
 4. Visualize 
 5. Model 
 6. Communicate 

```{r, Combining all Columns from above }
D1<-rbind(C_01_China_Long,C_02_NAFTA_Long,C_03_EU30_Long,C_04_RoW_Long)
```

## 5. GOAL 
Calculating Apparent Consumption 1: Calculations to get it by Year, Region and Sector (Accounting for Trade)
This data set has now been updated (on June 19th 2023) by Roland, and the "new model" that will be the iteration after this, will have a different set of data sets and calculations here. Here, I am referring to line 22 of the EoL tab of the spreadsheet. 

### PROCESS FLOW 
 1. Import
 2. Tidy
 3. **Transform**
 4. Visualize 
 5. Model 
 6. Communicate 

```{r, Apparent Consumption 1}

#############################################################
#############################################################
#  Combining E1 and G1                  ##
#############################################################
#############################################################

# Somehow the "sum" of all plastics types was not adding up to what was in the spreadsheet.
# So I imported the spreadsheet sum value 
#G2<-G1 %>% select(Region, Major_Market_Sector, Percentage) %>% 
  #group_by(Region, Major_Market_Sector) %>% 
  #summarise(Sum_Percentage=sum(Percentage))

E2.1<-D1 %>% filter(Type=="Sum")

#############################################################
#############################################################
#    End of Section                                        ##
#############################################################
#############################################################

#I did not do this step. 
#C5+G3 

G3<-B5 %>% inner_join(E2.1,
                      by=c("Region"="Region"))

#I got the 153.4 need for this - now * by China Transport sum. 
G3<-B5 %>% mutate(Converter_Consumption_1=
                    MT_Plastic_Prod_Resin+MT_Plastic_Import_Resin_no_Fiber+MT_Add)

G3<-G3 %>% select(Year, Region, Converter_Consumption_1)

G4<-G3 %>% inner_join(E2.1,
                      by=c("Region"="Region"))

G5<-G4 %>% mutate(Converter_Consump_2=Converter_Consumption_1*Percentage)
# Incorporate here the last thing. 

G6<-G5 %>% select(Year, Region, Major_Market_Sector, Converter_Consump_2)

# The one thing I don't have here is fiber. So lets get that in here.
G6.1 <- expand.grid(
  Year = c(2005:2020),
  Region = c("China","NAFTA","EU30","RoW"),
  Major_Market_Sector = c("Textiles")
)
G6.2<-B_02_Fiber %>% inner_join(G6.1,
                                by=c("Year"="Year","Region"="Region"))

colnames(G6.2)[3]<-"Converter_Consump_2"
G6.2<-G6.2 %>% select(Year, Region, Major_Market_Sector, Converter_Consump_2)

# Textiles is now part of the data frame! 
G7<-rbind(G6, G6.2)


# Making Major_Market_Sector Factor variable 
G7$Major_Market_Sector<- factor(G7$Major_Market_Sector, levels = 
                                  c("Transportation", 
                                    "Packaging", 
                                    "Building_Construction", 
                                    "Electrical_Electronic", 
                                    "Household_Leisure_Sports", 
                                    "Agriculture",
                                    "Textiles",
                                    "Others"))
# correct factor leveling 
levels(G7$Major_Market_Sector)

### G7 is the mother data set now 

```

Up until here we have all the variables and all the converter consumption, 
as portraryed in v12 (version 12) of the 20230227 of Global EoL treatment excel
sheet. 

For the new version I am adding Trade in the chunk below. Making it long form and then 
subtracting it from G7. 

```{r}
####
# CHINA TRADE 

F01_China<-AB_01_Trade_China %>% pivot_longer(cols=c("Transportation","Packaging","Building_Construction","Electrical_Electronic","Household_Leisure_Sports","Agriculture",
                                               "Textiles","Others"),
                                                 names_to='Major_Market_Sector',
                                                 values_to='MT_Trade')
F01.1 <- expand.grid(
  Year = c(2005:2020),
  Region = c("China"))

F01.2<-F01_China %>% inner_join(F01.1,
                                by=c("Year"="Year"))

####
# NAFTA TRADE 

F02_NAFTA<-AB_02_Trade_NAFTA %>% pivot_longer(cols=c("Transportation","Packaging","Building_Construction","Electrical_Electronic","Household_Leisure_Sports","Agriculture",
                                               "Textiles","Others"),
                                                 names_to='Major_Market_Sector',
                                                 values_to='MT_Trade')
F02.1 <- expand.grid(
  Year = c(2005:2020),
  Region = c("NAFTA"))

F02.2<-F02_NAFTA %>% inner_join(F02.1,
                                by=c("Year"="Year"))

####
# EU TRADE 

F03_EU<-AB_03_Trade_EU %>% pivot_longer(cols=c("Transportation","Packaging","Building_Construction","Electrical_Electronic","Household_Leisure_Sports","Agriculture",
                                               "Textiles","Others"),
                                                 names_to='Major_Market_Sector',
                                                 values_to='MT_Trade')
F03.1 <- expand.grid(
  Year = c(2005:2020),
  Region = c("EU30"))

F03.2<-F03_EU %>% inner_join(F03.1,
                                by=c("Year"="Year"))

####
# RoW TRADE

F04_Row<-AB_04_Trade_Row %>% pivot_longer(cols=c("Transportation","Packaging","Building_Construction","Electrical_Electronic","Household_Leisure_Sports","Agriculture",
                                               "Textiles","Others"),
                                                 names_to='Major_Market_Sector',
                                                 values_to='MT_Trade')
F04.1 <- expand.grid(
  Year = c(2005:2020),
  Region = c("RoW"))

F04.2<-F04_Row %>% inner_join(F04.1,
                                by=c("Year"="Year"))

F05<-rbind(F01.2,F02.2,F03.2, F04.2)

# Joing all trade information 
F05<-F05 %>% select(Year, Region, Major_Market_Sector, MT_Trade)

str(G7)
str(F05)
G7$Region<-as.factor(G7$Region)
F05$Major_Market_Sector<- factor(F05$Major_Market_Sector, levels = 
                                  c("Transportation", 
                                    "Packaging", 
                                    "Building_Construction", 
                                    "Electrical_Electronic", 
                                    "Household_Leisure_Sports", 
                                    "Agriculture",
                                    "Textiles",
                                    "Others"))

# Joining G7 with G8
G8<-G7 %>% inner_join(F05,
        by=c("Year"="Year", "Region"="Region","Major_Market_Sector"="Major_Market_Sector"))


```


We ar e now at Line 25 B of Eol Spreadsheet V12 
Apparent consumption from year 2005 to 2020 

```{r}

G9<-G8 %>% mutate(PC_Sector=Converter_Consump_2+MT_Trade)%>%
  mutate_at(5:6, round,3)

```

## 6. GOAL 
Calculating Apparent Consumption 2: Linear Regression of 2004 value. 

### PROCESS FLOW 
 1. Import
 2. Tidy
 3. **Transform**
 4. Visualize 
 5. Model 
 6. Communicate 

```{r, Apparent Consumption 2}
# Make a long form data set 
#############################################################
#############################################################
#    End of Section - Eol Line 42                          ##
# In this section we predict what year 2004 might have been given the past data ## 
#############################################################
#############################################################

#levels(G6.2$Region)

# Make a long form data set 
H0 <- expand.grid(
  Year = c(2004),
  Region = c("China","NAFTA","EU30","RoW"),
  Major_Market_Sector = c("Transportation","Packaging","Building_Construction","Electrical_Electronic",
                          "Household_Leisure_Sports","Textiles","Agriculture","Others")
)


# Just making sure I leave C6.2 intact 
H.1<-G9 %>% select(Year, Region, Major_Market_Sector, PC_Sector)
str(G9)
H.1$Major_Market_Sector<- factor(H.1$Major_Market_Sector, levels = 
                                  c("Transportation", 
                                    "Packaging", 
                                    "Building_Construction", 
                                    "Electrical_Electronic", 
                                    "Household_Leisure_Sports", 
                                    "Agriculture",
                                    "Textiles",
                                    "Others"))
str(H.1)
levels(H.1$Region)
H.1$Region<-as.factor(H.1$Region)

# This is the linear regression for predicting year 2004 
H2<-H.1 %>%
  group_by(Region, Major_Market_Sector) %>%         #.groups = "drop"
  summarize(PC_Sector = predict(lm(PC_Sector ~ Year), list(Year=2004))) %>%
  ungroup %>%
  select(Region, Major_Market_Sector, PC_Sector)%>% 
  mutate_at(3, round, 2)
str(H2)

# Stitch it together with HO so that I have a data frame 
H3<-H2%>% inner_join(H0, 
              by=c("Region"="Region", "Major_Market_Sector"="Major_Market_Sector"))

H4<-H3 %>% 
  select(Year,Region,Major_Market_Sector,PC_Sector)

H5<-rbind(H4,H.1)

# H5 is now the master data set 

```

## 7. GOAL 
Now we are doing imputations for China and NAFTA to be able to apply back wards on to H5 to get what the waste was since 1950. In the spread sheet this section is 1950~2004. Question for Roland has bee answered as to additives - they have already been included above. 

### PROCESS FLOW 
 1. Import
 2. Tidy
 3. **Transform**
 4. Visualize 
 5. Model 
 6. Communicate 

```{r, Apparent Consumption: Calculating Values from 1950-2004}

# 1950~2004 in Eol Spreadsheet 
#HH1<-read.csv("01_Data_Raw/14_1950-2004.csv") already fed in above. 
options(digits = 2)
China_2<-na_interpolation(AHH1$China)
NAFTA_lbs<-na_interpolation(AHH1$NAFTA_lbs)

China_2<-as.data.frame(China_2)
HH5<-cbind.data.frame(China_2,NAFTA_lbs)

HH5<-HH5 %>% 
  mutate(NAFTA=NAFTA_lbs/2204.62)

HH6<-cbind(HH5,AHH1) %>% 
  select(Year, China_2, NAFTA, EU30, RoW)

HH6$China_2<- round(HH6$China_2, 2)

# 1950~2004 in Eol Spreadsheet 
colnames(HH6)[colnames(HH6) == 'China_2'] <- 'China'

# making it long form
HH7<-HH6 %>% pivot_longer(cols=c("China","NAFTA","EU30","RoW"),
                                             names_to='Region',values_to='Total_MT_Plastic')

# Make a long form data set 
H0.1<- expand.grid(
  Year = c(1950:2004),
  Region = c("China","NAFTA","EU30","RoW"),
  Major_Market_Sector = c("Transportation","Packaging","Building_Construction","Electrical_Electronic",
                          "Household_Leisure_Sports","Textiles","Agriculture","Others")
)

HH8<-H0.1%>% right_join(HH7, 
                     by=c("Region"="Region", "Year"="Year"))
HH8<-as.data.frame(HH8)
# Making sure H5 goes untouched!
H6<-H5
str(H6)
str(HH8)
HH8$Region<-as.factor(HH8$Region)

HH9.2<-H4 %>% full_join(HH8,
                       by=c("Year"="Year","Region"="Region","Major_Market_Sector"="Major_Market_Sector"))
str(HH9.2)

#colnames(HH9.2)[colnames(HH9.2) == 'PC'] <- 'PC_Sector'

#write.csv(HH9.2, "/Users/dr.nivedita/Library/CloudStorage/OneDrive-Personal/04_Post-Doc/01.R_Code/06_Output\\HH9.2.csv")

```

## 8. GOAL 
Getting historic values for all regions and all sectors and all years.

### PROCESS FLOW 
 1. Import
 2. Tidy
 3. **Transform**
 4. Visualize 
 5. Model 
 6. Communicate 
 
 
```{r, Apparent Consumption for all years}

# Removing textiles 

HH9.3<-HH9.2 %>% filter(Major_Market_Sector!="Textiles")
H7<-H6%>% filter(Major_Market_Sector!="Textiles") %>% 
  filter(Year!="2004")

# With Carl's new Code! 

IA1<-HH9.3 %>% 
  arrange(desc(Major_Market_Sector), desc(Region), desc(Year)) %>%
  group_by(Region, Major_Market_Sector) %>%
  mutate(PC_Sector = Total_MT_Plastic * PC_Sector[[1]] / Total_MT_Plastic[[1]] )%>%
  ungroup()

################################################################################
################################################################################
#
#.    Combine 2020 + 2004  
#
################################################################################
################################################################################

IA2<-IA1 %>% select(-Total_MT_Plastic)
#colnames(IA2)[colnames(IA2) == 'PC_Sector'] <- 'PC'

IA3<-rbind(IA2,H7)

str(IA2)
str(H6)

#write.csv(IA3)
#write.csv(IA3.4)

#write.csv(IA3, "/Users/dr.nivedita/Library/CloudStorage/OneDrive-Personal/04_Post-Doc/01.R_Code/06_Output\\IA3.csv")

#write.csv(IA3.4, "/Users/dr.nivedita/Library/CloudStorage/OneDrive-Personal/04_Post-Doc/01.R_Code/06_Output\\IA3.4.csv")


################################################################################
################################################################################
 # IA3 is now the most important data frame 
################################################################################
################################################################################

```


Textiles was tricky. This will be separately added from V12. 

```{r}
# this is textiles which will be separately added 
#IA3.1<-HH9.2 %>% filter(Major_Market_Sector=="Textiles") # not correct so leave this alone. 

IA3.2<-H6%>% filter(Major_Market_Sector=="Textiles")

str(AD)

IA3.4<-rbind(IA3.2, AD)
str(IA3.4)
str(H5)
# Let check this out and see if it fits 

```


## VERSION JULY 7th 2023!
In this version we add textiles to the main data frame which is IA3. 
So IA3 + IA3.5 

Let's also make it smaller by summarizing by region 

```{r}

# join textiles to main data frame 

J_01<-rbind(IA3,IA3.4)

levels(J_01$Major_Market_Sector)
levels(IA3$Major_Market_Sector) 
levels(IA3$Year)


J_01$Major_Market_Sector<- factor(J_01$Major_Market_Sector, levels = 
                                  c("Transportation", 
                                    "Packaging", 
                                    "Building_Construction", 
                                    "Electrical_Electronic", 
                                    "Household_Leisure_Sports", 
                                    "Agriculture",
                                    "Textiles",
                                    "Others"))

str(J_01)

```

## FUTURE PROJECTING PRODUCTION 

```{r}

KA2 <- expand.grid(
  Year = c(2021:2049),
  Region = c("China","NAFTA","EU30","RoW"),
  Major_Market_Sector = c("Transportation","Packaging","Building_Construction","Electrical_Electronic",
                          "Household_Leisure_Sports","Textiles","Agriculture","Others"),
  PC_Sector=c(0)
)
KA2

# Predicting future plastic waste - lm function in stead of loess function

J_02<-J_01 %>%
  group_by(Region, Major_Market_Sector) %>%
  nest() %>%
  inner_join(KA2 %>% select(-PC_Sector) %>% group_by(Region, Major_Market_Sector) %>% nest(),
             by = c("Region", "Major_Market_Sector")) %>%
  mutate(model = data.x %>% map(~lm(PC_Sector ~ poly(Year,2), data=.)),
         PC_Sector = map2(model, data.y, predict)) %>%
  select(-data.x, -model) %>%
  unnest(cols= c(data.y, PC_Sector)) %>%
  bind_rows(J_01, .)

str(J_02)

```

## SHOW THIS PART TO ROLAND!! 

This is just checking the curve. Eu30 plastic packaging is going down and so is Textiles, anyways moving on! 

```{r}

J_03<-J_02 %>% filter(Region=="EU30") %>% 
  filter(Major_Market_Sector=="Packaging")

ggplot() + 
geom_line(data=J_03, aes(x=Year, y=PC_Sector), color='blue') + 
xlab("Year")+
ylab("Plastic Waste Generation in China lm ")+
ggtitle("China lm poly")

### cut and past this into a normal script and see what happens ### 

J_04<-ggplot() + 
  geom_line(data=J_02, aes(x=Year, y=PC_Sector), color='blue') + 
  xlab("Year")+
  ylab("Plastic Waste Generation in China lm ")+
  ggtitle("China lm poly")

J_04+
  facet_wrap(Region ~ Major_Market_Sector)

###.  ####             ####          ###.            ###    ########

```


## 9. GOAL 
Life time distribution section starts here. Since we do not have direct waste generation data, we use the LTD for each sector to know when plastic become waste. For Packageing the LTD is short - just 3 years. For Transportation the LTD is long - meaning that plastic used in the construction sector stays in the use phase for an average or 11 years. This is essentially calculating when something becomes waste.  

### PROCESS FLOW 
 1. Import
 2. Tidy
 3. **Transform**
 4. Visualize 
 5. Model 
 6. Communicate 

```{r, LifeTime Distribution Model Set up}

##   Make the Lifetime Distributions set up:  

options(digits = 9)

# Percentage that you might need later 
#I_01<-read.csv("01_Data_Raw/11_Sectors.csv") Already fed in above.

# Feeding in Lifetime Distribution 
#I_02<-read.csv("01_Data_Raw/12_Lifetime.csv")Already fed in above. 

# Make lifetime variables average and varience 
I_03<-AI_02 %>% mutate(mu=log(Average/sqrt(Variance/Average^2+1))) %>% 
  mutate(sigma=sqrt(log(Variance/Average^2+1)))

I_04_Year<- c(0.1, seq(1, 71, by=1))


#############################################################
#############################################################
##              LTD Transportation                         ##
#############################################################
#############################################################

options(digits = 2)
# Calculate the PDF using plnorm()
I_05_TransportationPDF<-plnorm(I_04_Year, meanlog = I_03$mu[1], 
                               sdlog = I_03$sigma[1])

J_A_PDF_Transport<-data.frame(I_04_Year,I_05_TransportationPDF) %>%
  mutate(Transportation= I_05_TransportationPDF - lag(I_05_TransportationPDF, 
                              default = first(I_05_TransportationPDF)))

G1Trans<-J_A_PDF_Transport[[3]][2:72]

#############################################################
#############################################################
#               LTD Packaging                              ##
#############################################################
#############################################################

options(digits = 2)
# Calculate the PDF using plnorm()
I_06_PackagingPDF<-plnorm(I_04_Year, meanlog = I_03$mu[2], 
                               sdlog = I_03$sigma[2])

J_B_PDF_Packaging<-data.frame(I_04_Year,I_06_PackagingPDF) %>%
  mutate(Packaging= I_06_PackagingPDF - lag(I_06_PackagingPDF, 
                                     default = first(I_06_PackagingPDF)))

G2Packaging<-J_B_PDF_Packaging[[3]][2:72]

#############################################################
#############################################################
#               Building and Construction                  ##
#############################################################
#############################################################

options(digits = 2)
# Calculate the PDF using plnorm()
I_07_BuildingPDF<-plnorm(I_04_Year, meanlog = I_03$mu[3], 
                          sdlog = I_03$sigma[3])

J_C_PDF_BuildingCons<-data.frame(I_04_Year,I_07_BuildingPDF) %>%
  mutate(Building_Construction= I_07_BuildingPDF - lag(I_07_BuildingPDF, 
                                  default = first(I_07_BuildingPDF)))

G3Building<-J_C_PDF_BuildingCons[[3]][2:72]

#############################################################
#############################################################
#               Electrical_Electronic                      ##
#############################################################
#############################################################

options(digits = 2)
# Calculate the PDF using plnorm()
I_08_ElectricPDF<-plnorm(I_04_Year, meanlog = I_03$mu[4], 
                         sdlog = I_03$sigma[4])

J_D_PDF_Electric<-data.frame(I_04_Year,I_08_ElectricPDF) %>%
  mutate(Electrical_Electronic= I_08_ElectricPDF - lag(I_08_ElectricPDF, 
                                    default = first(I_08_ElectricPDF)))

G4Electric<-J_D_PDF_Electric[2:72,3]

#############################################################
#############################################################
#               Household_Leisure                          ##
#############################################################
#############################################################

options(digits = 2)
# Calculate the PDF using plnorm()
I_09_HouseholdLeis<-plnorm(I_04_Year, meanlog = I_03$mu[5], 
                         sdlog = I_03$sigma[5])

J_E_PDF_Household<-data.frame(I_04_Year,I_09_HouseholdLeis) %>%
  mutate(Household_Leisure_Sports= I_09_HouseholdLeis - lag(I_09_HouseholdLeis, 
                                default = first(I_09_HouseholdLeis)))

G5House<-J_E_PDF_Household[2:72,3]

#############################################################
#############################################################
#               Agriculture.                               ##
#############################################################
#############################################################

options(digits = 2)
# Calculate the PDF using plnorm()
I_10_Agricul<-plnorm(I_04_Year, meanlog = I_03$mu[6], 
                           sdlog = I_03$sigma[6])

J_F_PDF_Agri<-data.frame(I_04_Year,I_10_Agricul) %>%
  mutate(Agriculture = I_10_Agricul - lag(I_10_Agricul, 
                                  default = first(I_10_Agricul)))

G6Agri<-J_F_PDF_Agri[[3]][2:72]

#############################################################
#############################################################
#               Others.                                    ##
#############################################################
#############################################################

options(digits = 2)
# Calculate the PDF using plnorm()
I_11_Othersl<-plnorm(I_04_Year, meanlog = I_03$mu[7], 
                     sdlog = I_03$sigma[7])

J_G_PDF_Other<-data.frame(I_04_Year,I_11_Othersl) %>%
  mutate(Others = I_11_Othersl - lag(I_11_Othersl, 
                                             default = first(I_11_Othersl)))

G7Others<-J_G_PDF_Other[[3]][2:72]

#############################################################
#############################################################
#               Textiles                                   ##
#############################################################
#############################################################

options(digits = 2)
# Calculate the PDF using plnorm()
I_12_Textiles<-plnorm(I_04_Year, meanlog = I_03$mu[8], 
                     sdlog = I_03$sigma[8])

J_H_Texti<-data.frame(I_04_Year,I_12_Textiles) %>%
  mutate(PDF_Textiles = I_12_Textiles - lag(I_12_Textiles, 
                                             default = first(I_12_Textiles)))

G8Textiles<-J_H_Texti[[3]][2:72]

```


## 10. GOAL 
Applying LTD to apparent consumption to get waste generation, by year, by sector, by region. 

### PROCESS FLOW 
 1. Import
 2. Tidy
 3. **Transform**
 4. Visualize 
 5. Model 
 6. Communicate 

```{r, Calculating Waste Gen}
################################################################################
################################################################################
#
#    Preparing to Calculate Waste Generation 
#
################################################################################
################################################################################
# you need to add textile from 2004 - 2020 
# for forgot to import it, so for now just do it without textiles but add it in later 

#KA1<-IA3 %>% filter(Major_Market_Sector!="Textile")
#str(KA1)

################################################################################
################################################################################
### After Meeting with Roland and Implementing Carl's Solution !! 
################################################################################
################################################################################

# Adding a data frame that extends the years out to KA1 
KA2.1 <- expand.grid(
  Year = c(1949:1900),
  Region = c("China","NAFTA","EU30","RoW"),
  Major_Market_Sector = c("Transportation","Packaging","Building_Construction","Electrical_Electronic",
                          "Household_Leisure_Sports","Textiles","Agriculture","Others"),
  PC_Sector=c(0)
)
KA2.1

KA3<-bind_rows(J_02,KA2.1)
str(KA3)
################################################################################
################################################################################
#
#    Calculating Waste Generation 
#
################################################################################
################################################################################

KB_1Transport<-KA3%>% 
 arrange(desc(Year)) %>% arrange((Region)) %>% arrange(desc(Major_Market_Sector)) %>% 
 group_by(Region) %>%
 filter(Major_Market_Sector=="Transportation") %>% 
 mutate(WasteGen= RcppRoll::roll_sum(PC_Sector, n=50, weights = G1Trans, align="left", 
                              na.rm = TRUE, normalize = FALSE, fill=NA))

KB_2Packaging<-KA3%>% 
  arrange(desc(Year)) %>% arrange((Region)) %>% arrange(desc(Major_Market_Sector)) %>% 
  group_by(Region) %>%
  filter(Major_Market_Sector=="Packaging") %>% 
  mutate(WasteGen= RcppRoll::roll_sum(PC_Sector, n=50, weights = G2Packaging, align="left", 
                                            na.rm = TRUE, normalize = FALSE, fill=NA))

KB_3Building<-KA3%>% 
  arrange(desc(Year)) %>% arrange((Region)) %>% arrange(desc(Major_Market_Sector)) %>% 
  group_by(Region) %>%
  filter(Major_Market_Sector=="Building_Construction") %>% 
  mutate(WasteGen= RcppRoll::roll_sum(PC_Sector, n=50, weights = G3Building, align="left", 
                                            na.rm = TRUE, normalize = FALSE, fill=NA))

KB_4Electric<-KA3%>% 
  arrange(desc(Year)) %>% arrange((Region)) %>% arrange(desc(Major_Market_Sector)) %>% 
  group_by(Region) %>%
  filter(Major_Market_Sector=="Electrical_Electronic") %>% 
  mutate(WasteGen= RcppRoll::roll_sum(PC_Sector, n=50, weights = G4Electric, align="left", 
                                            na.rm = TRUE, normalize = FALSE, fill=NA))

KB_5House<-KA3%>% 
  arrange(desc(Year)) %>% arrange((Region)) %>% arrange(desc(Major_Market_Sector)) %>% 
  group_by(Region) %>%
  filter(Major_Market_Sector=="Household_Leisure_Sports") %>% 
  mutate(WasteGen= RcppRoll::roll_sum(PC_Sector, n=50, weights = G5House, align="left", 
                                            na.rm = TRUE, normalize = FALSE, fill=NA))

KB_6Agri<-KA3%>% 
  arrange(desc(Year)) %>% arrange((Region)) %>% arrange(desc(Major_Market_Sector)) %>% 
  group_by(Region) %>%
  filter(Major_Market_Sector=="Agriculture") %>% 
  mutate(WasteGen= RcppRoll::roll_sum(PC_Sector, n=50, weights = G6Agri, align="left", 
                                            na.rm = TRUE, normalize = FALSE, fill=NA))

KB_7Other<-KA3%>% 
  arrange(desc(Year)) %>% arrange((Region)) %>% arrange(desc(Major_Market_Sector)) %>% 
  group_by(Region) %>%
  filter(Major_Market_Sector=="Others") %>% 
  mutate(WasteGen= RcppRoll::roll_sum(PC_Sector, n=50, weights = G7Others, align="left", 
                                            na.rm = TRUE, normalize = FALSE, fill=NA))

levels(KA3$Major_Market_Sector)

KB_8Textiles<-KA3%>% 
  arrange(desc(Year)) %>% arrange((Region)) %>% arrange(desc(Major_Market_Sector)) %>% 
  group_by(Region) %>%
  filter(Major_Market_Sector=="Textiles") %>% 
  mutate(WasteGen= RcppRoll::roll_sum(PC_Sector, n=50, weights = G8Textiles, align="left", 
                                            na.rm = TRUE, normalize = FALSE, fill=NA))

```


## 11. GOAL 
Preparing Waste Generation data-frame for End-of-Life (EOL). 
Ignore the warnings here. 

### PROCESS FLOW 
 1. Import
 2. Tidy
 3. **Transform**
 4. Visualize 
 5. Model 
 6. Communicate 

```{r, Waste Generation to End-of_Life}
################################################################################
################################################################################
#
#    Waste Gen to EOL 
#
################################################################################
################################################################################


KC_1Transport<-KB_1Transport %>%
  group_by(Region) %>% 
  mutate(Year_2=c(2050:1901)) %>% 
  select(Year_2, Region, Major_Market_Sector,WasteGen) %>% 
  group_by(Region) %>% 
  filter(Year_2==(2050:1971))

KC_2Packaging<-KB_2Packaging %>%
  group_by(Region) %>% 
  mutate(Year_2=c(2050:1901)) %>% 
  select(Year_2, Region, Major_Market_Sector,WasteGen) %>% 
  group_by(Region) %>% 
  filter(Year_2==(2050:1971))

KC_3Building<-KB_3Building %>%
  group_by(Region) %>% 
  mutate(Year_2=c(2050:1901)) %>% 
  select(Year_2, Region, Major_Market_Sector, WasteGen) %>% 
  group_by(Region) %>% 
  filter(Year_2==(2050:1971))

KC_4Electric<-KB_4Electric %>%
  group_by(Region) %>% 
  mutate(Year_2=c(2050:1901)) %>% 
  select(Year_2, Region, Major_Market_Sector,WasteGen) %>% 
  group_by(Region) %>% 
  filter(Year_2==(2050:1971))

KC_5House<-KB_5House %>%
  group_by(Region) %>% 
  mutate(Year_2=c(2050:1901)) %>% 
  select(Year_2, Region, Major_Market_Sector,WasteGen) %>% 
  group_by(Region) %>% 
  filter(Year_2==(2050:1971))

KC_6Agri<-KB_6Agri%>%
  group_by(Region) %>% 
  mutate(Year_2=c(2050:1901)) %>% 
  select(Year_2, Region, Major_Market_Sector,WasteGen) %>% 
  group_by(Region) %>% 
  filter(Year_2==(2050:1971))

KC_7Other<-KB_7Other%>%
  group_by(Region) %>% 
  mutate(Year_2=c(2050:1901)) %>% 
  select(Year_2, Region, Major_Market_Sector,WasteGen) %>% 
  group_by(Region) %>% 
  filter(Year_2==(2050:1971))

KC_8Textiles<-KB_8Textiles%>%
  group_by(Region) %>% 
  mutate(Year_2=c(2050:1901)) %>% 
  select(Year_2, Region, Major_Market_Sector,WasteGen) %>% 
  group_by(Region) %>% 
  filter(Year_2==(2050:1971))

KD<-rbind(KC_1Transport,KC_2Packaging,KC_3Building,
          KC_4Electric,KC_5House,KC_6Agri,KC_7Other,KC_8Textiles)

```

## Visualizing Waste Gen 

```{r}
K_04<-ggplot() + 
  geom_line(data=KD, aes(x=Year_2, y=WasteGen), color='blue') + 
  xlab("Year")+
  ylab("Plastic Waste Generation in China lm ")+
  ggtitle("China lm poly")

K_04+
  facet_wrap(Region ~ Major_Market_Sector)

```

## Adding polymer Data into the mix

 
```{r}
#D1<-D1 %>% filter(Type!="Sum")


#############################################################
#############################################################

##### CHINA #####

C_01_China_Long2<-AC_01_China2 %>% pivot_longer(cols=c('LLDPE_LDPE',"HDPE","PP","PS","PVC","PET","PUR","Other.Thermoplastics","Other.Thermosets","Sum"),
                                             names_to='Type',
                                             values_to='Percentage')
C_01_China_Long2<-C_01_China_Long2 %>% 
  add_column(Region = "China")

C_01_China_Long2<-C_01_China_Long2[c("Region","Major_Market_Sector","Type","Percentage")]


##### NAFTA #####
C_02_NAFTA_Long2<-AC_02_NAFTA2 %>% pivot_longer(cols=c('LLDPE_LDPE',"HDPE","PP","PS","PVC","PET","PUR","Other.Thermoplastics","Other.Thermosets","Sum"),
                                             names_to='Type',
                                             values_to='Percentage')
C_02_NAFTA_Long2<-C_02_NAFTA_Long2 %>% 
  add_column(Region = "NAFTA")

C_02_NAFTA_Long2<-C_02_NAFTA_Long2[c("Region","Major_Market_Sector","Type","Percentage")]


##### EU30 #####

C_03_EU30_Long2<-AC_03_Europe2 %>% pivot_longer(cols=c('LLDPE_LDPE',"HDPE","PP","PS","PVC","PET","PUR","Other.Thermoplastics","Other.Thermosets","Sum"),
                                             names_to='Type',
                                             values_to='Percentage')
C_03_EU30_Long2<-C_03_EU30_Long2 %>% 
  add_column(Region = "EU30")

C_03_EU30_Long2<-C_03_EU30_Long2[c("Region","Major_Market_Sector","Type","Percentage")]

##### RoW #####

C_04_RoW_Long2<-AC_04_Row2 %>% pivot_longer(cols=c('LLDPE_LDPE',"HDPE","PP","PS","PVC","PET","PUR","Other.Thermoplastics","Other.Thermosets","Sum"),
                                         names_to='Type',
                                         values_to='Percentage')
C_04_RoW_Long2<-C_04_RoW_Long2 %>% 
  add_column(Region = "RoW")

C_04_RoW_Long2<-C_04_RoW_Long2[c("Region","Major_Market_Sector","Type","Percentage")]

D12<-rbind(C_01_China_Long2,C_02_NAFTA_Long2,C_03_EU30_Long2,C_04_RoW_Long2)

KD1<- KD %>% inner_join(D12, 
           by=c('Region','Major_Market_Sector'))

KD2<-KD1 %>% mutate(WasteGen_2=WasteGen*Percentage) %>% 
  filter(Type!="Sum")

KD3<-KD2 %>% select(-Percentage) %>% 
  pivot_wider(names_from=Type, 
              values_from=c(WasteGen_2)) 

#write.csv(KD3, "/Users/dr.nivedita/Library/CloudStorage/OneDrive-Personal/04_Post-Doc/01.R_Code/06_Output\\KD3.csv")


```


## DEALINg with the EOL DATA 

```{r}

#Get Rid of Percentage Sign 
(AKE_Eol_China <- data.frame(sapply(AKE_Eol_China, function(x) as.numeric(gsub("%", "", x)))))
(AKE_Eol_EU <- data.frame(sapply(AKE_Eol_EU, function(x) as.numeric(gsub("%", "", x)))))
(AKE_Eol_NAFTA <- data.frame(sapply(AKE_Eol_NAFTA, function(x) as.numeric(gsub("%", "", x)))))
(AKE_Eol_Row <- data.frame(sapply(AKE_Eol_Row, function(x) as.numeric(gsub("%", "", x)))))

# Add Region 
AKE_Eol_China <- AKE_Eol_China %>% mutate(Region=c("China"))
AKE_Eol_EU <-AKE_Eol_EU %>% mutate(Region=c("EU30"))
AKE_Eol_NAFTA<-AKE_Eol_NAFTA %>% mutate(Region=c("NAFTA"))
AKE_Eol_Row<-AKE_Eol_Row %>% mutate(Region=c("RoW"))

#Make long form 
LA1<-AKE_Eol_China %>% pivot_longer(cols=c('Recycling',"Incineration","Landfill","Mismanaged"),
                                          names_to='EOL',
                                          values_to='Percentage')

LA2<-AKE_Eol_EU %>% pivot_longer(cols=c('Recycling',"Incineration","Landfill","Mismanaged"),
                                          names_to='EOL',
                                          values_to='Percentage')

LA3<-AKE_Eol_NAFTA %>% pivot_longer(cols=c('Recycling',"Incineration","Landfill","Mismanaged"),
                                          names_to='EOL',
                                          values_to='Percentage')

LA4<-AKE_Eol_Row %>% pivot_longer(cols=c('Recycling',"Incineration","Landfill","Mismanaged"),
                                          names_to='EOL',
                                          values_to='Percentage')

# Joining Long form 
LA5<-rbind(LA1,LA2,LA3,LA4)

LA5.1<-LA5 %>% 
  pivot_wider(names_from=EOL, 
              values_from=c(Percentage)) 

#write.csv(LA5, "/Users/dr.nivedita/Library/CloudStorage/OneDrive-Personal/04_Post-Doc/01.R_Code/06_Output\\LA5.csv")

```


## EOL 

Doing as Sam said - (total waste * EOL percent in a region ~ year)


```{r}
# Getting KD into the right format to apply end of life 
levels(KD$Major_Market_Sector)

######## 
######## Re-check this !!!!! - Roland 18th July 2023 

# Previously LB5
KD4 <-KD %>% group_by(Year_2, Region) %>% summarize(Prim_Waste=sum(WasteGen))
######## 
########
```

This still does not work for predicting EOL. 
So I am going to go with my original idea of keeping all 2006 values for anything pre - 2006 
and keeping all 2021 values for anything after 2021 to 2050. See below. 

# UPWARD - 2021 - 2050 FOR ALL SECTORS 


```{r}

#UPWARDS FOR ALL 

MA1<- expand.grid(
  Year_2 = c(2021:2050),
  Region = c("China","NAFTA","EU30","RoW"),
  EOL = c("Recycling", "Incineration","Landfill","Mismanaged"),
  Percentage=c(NA)
)

MA3<-rbind(LA5, MA1)

MA4<-MA3 %>% arrange(desc(Year_2)) %>%
  group_by(Region, EOL) %>% 
  fill(Percentage, .direction = 'up')

```


# DOWNWARD FOR ALL SECTORS - 1970 - 1999 FOR ALL SECTORS 


```{r}

MA2<- expand.grid(
  Year_2 = c(1970:1998),
  Region = c("China","NAFTA","EU30","RoW"),
  EOL = c("Recycling", "Incineration","Landfill","Mismanaged"),
  Percentage=c(NA)
)

MA2.3<-rbind(MA4,MA2)%>%
  arrange(Year_2) %>% arrange(Region) %>% arrange(EOL)

MA2.3$Percentage[MA2.3$Year_2 >= 1970 & MA2.3$Year_2 <= 1974] <- 0

MA5 <- MA2.3 %>%
        mutate( Percentage = na.approx(Percentage))

MA5.1<-MA5 %>% inner_join(KD4,
                   by=c("Region"="Region","Year_2"="Year_2"))

```

## VISUALIZING PLOTS 

```{r}

ggplot(data = MA5, aes(x = Year_2, y = Percentage)) +
  geom_point()

```

# JOIN BOTH = DONE !
# RECYCLING ONLY 

### 
RECYCLING 
### 

This part ends the first part of the recycling section. Applying Sam's Recycling Help Nivi code to this section of the data! 

##

```{r}

MA6<-MA5.1 %>% filter(EOL=="Recycling") %>%
  arrange(Year_2) %>% arrange(Region)

Target_MB_1<-MA6

# Setup calculations
get_t_waste <- function (target) { target$Prim_Waste + target$Sec_Waste }
get_sec_material <- function (target) { target$T_Waste * target$Percentage/100}

build_shifted_recycling <- function (target) {
  # Seed
  target$Sec_Waste <- 0
  target$T_Waste <-get_t_waste(target)
  target$Sec_Material <-get_sec_material(target)
  
  # Shift forward
  target$Sec_Waste <- lag(target$Sec_Material, 3)
  target$Sec_Waste[is.na(target$Sec_Waste)] <- 0
  
  # Recompute after shifting
  target$T_Waste <- get_t_waste(target)
  
  return(target)
}

Target_MB_2 = NULL
on_first_result = TRUE;
for (region in list('China', 'NAFTA', 'EU30', 'RoW')) {
  new_result = build_shifted_recycling(Target_MB_1[Target_MB_1$Region == region,])
  
  if (on_first_result) {
    Target_MB_2 = new_result
    on_first_result = FALSE
  } else {
    Target_MB_2 = rbind(Target_MB_2, new_result)
  }
}

#write.csv(Target_MB_2, "/Users/dr.nivedita/Library/CloudStorage/OneDrive-Personal/04_Post-Doc/01.R_Code/06_Output\\Target_MB_2.csv")

```

## ADDING RECYCLING INTO MAIN DATA FRAME WITH ALL EOL FATES 

```{r}

# EOL only Recycling 
TB<-Target_MB_2 %>% select(Year_2, Region, EOL, Sec_Waste)
colnames(TB)[colnames(TB) == 'Sec_Waste'] <- 'Prim_Waste'

# All EOL  excluding recycling 
TB1<-MA5.1 %>% filter(EOL!="Recycling") %>% 
  select(Year_2, Region,EOL,Prim_Waste)

# Join Together
TB2<-rbind(TB1,TB)

```


# CONSUMPTION BY POLYMER TYPE 


```{r}

# Consumption by Polymertype 

TB3<-KA3 %>% inner_join(D12, 
        by=c('Region'="Region","Major_Market_Sector"="Major_Market_Sector")) %>% 
  filter(Type!="Sum")

TB3<-TB3 %>% mutate(PC_Polymer=PC_Sector*Percentage)

TB4<-TB3 %>% select(Year, Region, Major_Market_Sector, Type, PC_Polymer)

```

# CONSUMPTION BY POLYMER TYPE #2 WITHOUT MARKET SECTOR 

```{r}
#TB5 <-KA3 %>% select(-Major_Market_Sector) %>% 
  #group_by(Year, Region) %>% summarize(PC_Total=sum(PC_Sector))

#TB5.1<-TB5 %>% inner_join(D12, 
        #by=c('Region'="Region")) %>% 
  #filter(Type!="Sum")

```



# Final Asks 

```{r}
# Sam's ask 1 = Waste Gen - year, region, market_sector, polymer type
# Waste_Gen_2 is waste for each polymer type in Million Metric Tons
KD3 
str(KD3)

# Sam's ask 2 = Consumption - year, region, market_sector
# PC_sector is consumption in Million Metric Tons
KA3
 
# Sam's ask 3 = Waste Gen - year, region, EOL type
# EOL_Waste_5 is waste for each EOL fate in Million Metric Tons
TB2

#ggplot(data = TB2, aes(x = Year_2, y = Prim_Waste)) +
  #geom_point()

# Sam's ask 4 = Consumption - year, region, market_Sector, polymer type
TB4 

```


